Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-08 mu/article/article.tex
Changing working station: Description of V_{s^z} for up.

\begin{figure}[b]
    \centering
    \subfigure[\, \label{fig:up-vaz-rag-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
    \\
    \subfigure[\, \label{fig:up-vaz-rag-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}

@@

We first present two energy ranges for the \emph{up} structure, the first for an
incoming energy beam from 0.0\,eV to 0.2\,eV where the absolute maximum of the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response is obtained and the
second for an energy range from 1.80\,eV to 2.1\,eV where two local maxima are
found.
% 
In Fig. \ref{fig:up-3d-vsz} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in the
Eq. \eqref{eq:vab} for the \emph{up} structure. In the figure we have that the
onset of the response starts when the energy of the incoming beam is the same of
the gap energy.
% 
From this figure we obtained that the zone where the maximum response is held
corresponds to a energy range of the incident beam from 0.084\,eV to 0.093\,eV
and polarization angles $\alpha$ between $30^{\circ}$ and $45^{\circ}$. Also two
local maxima are held for same polarization angles but for an energy range of
the incoming beam between 1.90\,eV and 2.05\,eV.
% 
In the top frames of Figs.\ref{fig:up-vaz-rag-1} and \ref{fig:up-vaz-rag-2} we
present in solid lines the result of evaluate
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the left scale, fixing
the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively, for
which the response is maximized for the \emph{up} structure. In the same figures
and frames we present in dashed lines, related to the right scale, the
corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom
frames of those figures the corresponding components
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$.
Also we present two circled and square boxes indicating the value where the
angles of the spin velocity is parallel and perpendicular and the the
corresponding arrows is directed to the value of the response corresponding to
those angles.

>>>>

\begin{figure}[t]
    \centering
    \subfigure[\, \label{fig:up-vaz-rag-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
    \\
    \subfigure[\, \label{fig:up-vaz-rag-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}

@@

We first present two energy ranges for the \emph{up} structure, the first for an
incoming energy beam from 0.0\,eV to 0.2\,eV where the absolute maximum of the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response is obtained and the
second for an energy range from 1.80\,eV to 2.1\,eV where two local maxima are
found.
% 
In Fig. \ref{fig:up-3d-vsz} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in the
Eq. \eqref{eq:vab} for the \emph{up} structure. In the figure we have that the
onset of the response starts when the energy of the incoming beam is the same of
the gap energy.
% 
From this figure we obtained that the zone where the maximum response is held
corresponds to a energy range of the incident beam from 0.084\,eV to 0.093\,eV
and polarization angles $\alpha$ between $30^{\circ}$ and $45^{\circ}$. Also two
local maxima are held for same polarization angles but for an energy range of
the incoming beam between 1.90\,eV and 2.05\,eV.
% 
In the top frames of Figs.\ref{fig:up-vaz-rag-1} and \ref{fig:up-vaz-rag-2} we
present in solid lines the result of evaluate
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the left scale, fixing
the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively, for
which the response is maximized for the \emph{up} structure. In the same figures
and frames we present in dashed lines, related to the right scale, the
corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom
frames of those figures the corresponding components
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$.
Also we present two circled and square boxes indicating the value where the
angles of the spin velocity is parallel and perpendicular and the the
corresponding arrows is directed to the value of the response corresponding to
those angles.
% 
From Fig. \ref{fig:up-vaz-rag-1} we have that the maximum response is obtained
for an incoming beam with energy of 0.088\,eV and polarization angle of
$40^{\circ}$ resulting in a value of 37.4\,Km/s coming from the contribution of
the components $\mathcal{V}^{\mathrm{xz}}(\omega)=39.8$\,Km/s and
$\mathcal{V}^{\mathrm{yz}}(\omega)=87.2$\,Km/s and being this response the
absolute maximum of the spin velocity polarized in the $\mathrm{z}$ direction
for the \emph{up} structure and corresponding a velocity angle
$\gamma_{\mathrm{z}}(\omega)=65^{\circ}$ on the $xy$ plane.
% 
In the same figure the green circled box indicates the angle 
% cicled green box; deviation?

% From the same figure we have that for a polarization angle $\alpha=65^{\circ}$
% the response is directed in the same angle direction being collinear and
% resulting in a value of
% $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=82.3$\,Km/s;
